## Summary 
```{r}
#| include: false
library(tidyverse)
library(knitr)
```

In this project we try to predict whether an online shopping session will end in a purchase. That’s useful for understanding which users are likely to buy and for supporting efforts on how to improve conversion rates and user experience.

We use the UCI Online Shoppers Purchasing Intention dataset. It’s public and has about 12,330 sessions. Each row is one session, and we have information on how many admin vs product pages they saw, time on site, bounce and exit rates, and session data like month and whether it was a weekend. The target variable is Revenue which is a binary variable, indicating whether the session ended in a purchase. We downloaded the data from the web, cleaned it up (factors, missing values, etc.), and did an 80/20 train–test split.

We did some EDA with summary tables and visualizations, then fit a Lasso logistic regression and looked at the confusion matrix and ROC curve.

```{r}
#| include: false
metrics <- read_csv("results/model_metrics.csv", show_col_types = FALSE)

precision <- metrics %>% filter(Metric == "Test Precision") %>% pull(Value)
AUC <- metrics %>% filter(Metric == "Test AUC") %>% pull(Value)
recall <- metrics %>% filter(Metric == "Test Recall") %>% pull(Value)
```

The model gets `r round(AUC, 3)` AUC and `r round(precision, 3)` precision on the test set. It is very reliable when predicting a purchase but struggles to find them all (`r round(recall, 3)` recall). This corresponds to a very precise but low sensitivity model. 