## Methods and Results 

### Imports 
```{r}
library(tidyverse)
library(glmnet)
library(scales)
library(pROC)
library(caret)
```
### Load Data

To start off the analysis, we first need to load all the data from the internet. We will also split the data into features and targets right now for convenience.

```{r}
csv_path <- "data/raw/online_shoppers_purchasing_intention_dataset.csv"
raw_shoppers_data <- read_csv(csv_path)

raw_shoppers_features <- raw_shoppers_data %>% select(-Revenue)
raw_shoppers_targets <- raw_shoppers_data %>% select(Revenue)
```

Let us quickly get a brief overview of the data to make sure it was loaded properly.

```{r}
dim(raw_shoppers_features)
dim(raw_shoppers_targets)
```

### Dataset Description
With the data loaded successfully, we can examine the available features. This information is referenced from the official data source (UCI Machine Learning Repository: Online Shoppers Purchasing Intention Dataset).
Each row/data point represents one user session.

::: {#tbl-numerical-feature-description}

| Feature  | Type | Feature Description |
|----------------|-------------|------------------------|
| Administrative  | Integer | Number of administrative pages viewed per session |
| Administrative_Duration  | Integer | Total time spent on administrative pages per session |
| Informational  | Integer | Number of informational pages viewed per session |
| Informational_Duration  | Integer | Total time spent on informational pages per session |
| ProductRelated  | Integer | Number of product related pages viewed per session |
| ProductRelated_Duration  | Continuous | Number of product related pages viewed per session |
| BounceRates  | Continuous | Inverse of engagement rate (From Google Analytics) |
| ExitRates  | Continuous | Last page before stopping the user session (From Google Analytics) |
| PageValues  |  Integer | Average value each page contributes to the user session (From Google Analytics) |
| SpecialDay  | Integer | Closeness of the site visited date to a "special date" where purchase are more likely |

Numerical Features
:::

::: {#tbl-categorical-feature-description}

| Feature  | Feature Description |
|----------------|-------------|
| Month  | Month of session |
| OperatingSystems | Operating system used for session |
| Browser  | Browser used for session |
| Region | Geographic region of session |
| TrafficType | Traffic source of session (banner, direct, SMS, etc.) |
| VisitorType | Visitor type of session (New, Returning, etc.) |
| Weekend  | Binary value indicating the session occurred on a weekend |

Categorical Features
:::

::: {#tbl-target-variable-description}

| Target Variable  | Variable Description |
|----------------|-------------|
| Revenue  | Binary class label indicating whether the user session ended in a purchase |

Target Variable
:::

Knowing the expected data types of each feature, we can proceed with data cleaning to prepare for EDA and analysis.
